Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-10 presentation/presentation.tex
Adding guaranteeing CF coloring slides

  \section{CF Coloring for General Graphs}
  \subsection{Guaranteeing CF k-Colorability}
  \begin{frame}
    \frametitle{Guaranteeing CF k-Colorability}

@@

  \begin{frame}
    \frametitle{Guaranteeing CF k-Colorability}

>>>>

  \section{CF Coloring for General Graphs}
  \subsection{Guaranteeing CF k-Colorability}
  \begin{frame}
    \frametitle{Guaranteeing Conflict-Free k-Colorability}

@@

  \begin{frame}
    \frametitle{Guaranteeing Conflict-Free k-Colorability}

    % \begin{textblock*}{\examplewidth}(1cm,1.4cm) % {block width} (coords)
    % \end{textblock*}

    \begin{textblock*}{14cm}(1cm, 1.6cm) % {block width} (coords)
      Let's demonstrate meeting this criterion on a graph for the simplest case, $k=1$:
    \end{textblock*}

    \begin{textblock*}{15cm}(0.5cm, 2.1cm) % {block width} (coords)
      \only<1>{
        \begin{figure}
         \centering
         \includegraphics[width=6cm]{../figures/criterion.pdf}
         \caption{A simple, undirected graph $G$}
       \end{figure}
      }

      \only<2>{
        \vspace{0.25cm}
        \begin{columns}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                 \centering
                 \includegraphics[width=6cm]{../figures/criterion.pdf}
                 \caption{A simple, undirected graph $G$}
               \end{figure}
            \end{center}
          \end{column}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
                \caption{Graphs $K_{3}$ and $K_{4}^{-3}$}
              \end{figure}
            \end{center}
          \end{column}
        \end{columns}
      }

      \only<3>{
        \vspace{0.25cm}
        \begin{columns}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                 \centering
                 \includegraphics[width=6cm]{../figures/criterion-minor.pdf}
                 \caption{A simple, undirected graph $G$}
               \end{figure}
            \end{center}
          \end{column}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
                \caption{Graphs $K_{3}$ and $K_{4}^{-3}$}
              \end{figure}
            \end{center}
          \end{column}
        \end{columns}
      }
    \end{textblock*}

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor. A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
    \end{textblock*}
